---
title: "IMDB 'Top 250' dataset"
output:
  html_document:
    df_print: paged
---

```{r, chunk-setup, include=FALSE}
# include=FALSE means it is running, but invisible ...
knitr::opts_chunk$set(echo = TRUE);
knitr::opts_chunk$set(warning = FALSE);
knitr::opts_chunk$set(message = FALSE);

data.path = "R:/WSU_STATS419_FALL2020/modules/imdb/2020-09/dataframes/";
imdb.path = "C:/_git_/MonteShaffer/humanVerseWSU/humanVerseWSU/inst/extdata/";

backup.path = "C:/_git_/MonteShaffer/humanVerseWSU/compiling/raw-data/";

```

# Motivation
From Wikipedia: "IMDb is an online database of information related to films, television programs, home videos, video games, and streaming content online – including cast, production crew and personal biographies, plot summaries, trivia, ratings, and fan and critical reviews." (October 3, 2020)

This dataset utilizes **only films**. [Underline would be nice here, wouldn't it!?!]

## Official IMDB datasets
IMDB does make some of its data available for direct download <https://www.imdb.com/interfaces/>.  However, the data fields are a bit wanting.

## September 2020 Custom dataset

### Seed Top 250 (September 2020)

Using this URL as a seed <https://www.imdb.com/chart/top>, I collected the top 250 movies. 

```{r, chunck-top250, include=TRUE}

movies.seed.file = paste0(data.path, "movies.sourced.by.top250.txt");
movies.seed.df   = utils::read.csv(movies.seed.file, 
                                      header=TRUE, quote="", sep="|");

dim(movies.seed.df);

movies.seed.vector = as.character( unlist(movies.seed.df) );

head( movies.seed.vector );

# saveRDS(movies.seed.vector,
#           file= paste0(imdb.path, "imdb/top250.seed.movies.rds") );


```

For each movie, I collected and cached the summary `filmInfo` page: e.g.,  <https://www.imdb.com/title/tt0111161>

A movie has a unique id which I call ``ttid`.  Of note on this page:

* The "oneliner":    A paragraph describing the movie.

* The "creatives":  Directors, Writers, and generally Top-3 actors.  Each person has a "name id" or `nmid` that links them to other projects (I focus on films).

* Top-15 actors:  Actor name (with `nmid`) and character name(s) in the film `ttid`.

* Primary facts:  Rated ("R"), Minutes, Genre(s), Votes, Gross (Millions), Metascore, Stars ("9.3/10"), and so on.

* Other Info:  See Details, Box Office, Company Credits, Technical Specs (only available on the summary `filmInfo` page.

#### Top Actors in Top 250 (September 2020)

For each of these 250 films, I collected the 15 top actors.  At most, that would give me 3750 actors, but there are duplicates.

```{r, chunck-top250-actors-list, include=TRUE}

actors.seed.file = paste0(data.path, "actors.top250.txt");
actors.seed.df   = utils::read.csv(actors.seed.file, 
                                      header=TRUE, quote="", sep="|");

dim(actors.seed.df);

actors.seed.vector = as.character( unlist(actors.seed.df) );

head( actors.seed.vector );

# saveRDS(actors.seed.vector,
#           file= paste0(imdb.path, "imdb/top250.seed.actors.rds") );


```

From the 250 top movies, we have 3,092 actors.  For each actor, we grab the actor information page based on the name id `nmid`; e.g., <https://www.imdb.com/name/nm0000209/> for Tim Robbins.

From the `personInfo` page:

* Name

* Starmeter rank (e.g., 5000) and delta (57 means up 57, -57 means down 57).

* Top-3 Roles:  Actor,Producer,Director

* Bio

* Birth info

* Death info

```{r, chunck-top250-actors, include=TRUE}
library(humanVerseWSU);
  ##' TOO INSTALL:  
  ##'   Requires Rtools ... https://cran.r-project.org/bin/windows/Rtools/
  # library(devtools);
  # detach(package:humanVerseWSU);
  # install_github("MonteShaffer/humanVerseWSU/humanVerseWSU");
  # library(humanVerseWSU);

actors.info.file = paste0(data.path, "actors.info.by.top250.txt");
actors.info.df   = utils::read.csv(actors.info.file, 
                                          header=TRUE, quote="", sep="|");




actors.info.df = moveColumnsInDataFrame(actors.info.df, 
                                              "bio", "after", "starmeter.delta");
  

dim(actors.info.df);  # 3092   10

head(actors.info.df, n=10);


# saveRDS(actors.info.df,
#           file= paste0(imdb.path, "imdb/top250.actors.info.rds") );


```

#### All movies from all actors from Top 250 Movies (September 2020)

For these 3,092 unique actors, a search is performed:
`https://www.imdb.com/filmosearch/?explore=title_type&role={nmid}&ref_=filmo_ref_typ&sort=num_votes,desc&mode=detail&page={page}&title_type=movie`

Where the `{nmid}` is replaced with the actor's unique `nmid` and all relevant pages are harvested.  For the given actor `nmid`, the relevant `ttid` and `rank` is recorded (this search is sorted by popularity, number of votes).  We merge this with the `name` and `character` information to build `top250.gluetable.

```{r, chunck-top250-actors-to-movies, include=TRUE}



glue.file = paste0(backup.path, "top250.actors.movies.rds");

if(!file.exists(glue.file))
{
  
actors.movies.file = paste0(data.path, "actors.movies.top250.txt");
actors.movies.df   = utils::read.csv(actors.movies.file, 
                                          header=TRUE, quote="", sep="|");

character.info.file = paste0(data.path, "movies.actors.characters.txt");
character.info.df   = utils::read.csv(character.info.file, 
                                          header=TRUE, quote="", sep="|");




actors.movies.df = moveColumnsInDataFrame(actors.movies.df, 
                                              "ttid", "after", "nmid");

actors.movies.df$name = "NA";
actors.movies.df$character = "NA";

na = dim(actors.movies.df)[1];  # 129300    

# expensive loop
for(i in 1:na)
  {
  row = actors.movies.df[i,];
  my.ttid = row$ttid;
  my.nmid = row$nmid;
  
  percent = sprintf("%.2f",100*i/na);
    print(paste0(percent,"%         :: ",i," of ",na," --->  ttid: ",my.ttid," nmid: ",my.nmid)); flush.console();

  my.match = character.info.df[ character.info.df$ttid==my.ttid &
                                character.info.df$nmid==my.nmid, ];
  if(dim(my.match)[1] > 0)
    {
    actors.movies.df$name[i] = my.match$name;
    actors.movies.df$character[i] = my.match$character;
    }
  }

###############################################

# saveRDS(actors.movies.df,
#           file= paste0(backup.path, "top250.actors.movies.rds") );





} else {
  
actors.movies.df = readRDS(paste0(backup.path, "top250.actors.movies.rds") );
   
}
  



dim(actors.movies.df);  # 129300      5

length( unique( actors.movies.df$ttid ) ); # 68784


head(actors.movies.df, n=10);


actors.table = as.data.frame( table(actors.movies.df$nmid) );
actors.table = sortDataFrameByNumericColumns(actors.table, "Freq");
colnames(actors.table) = c("nmid","freq");

# saveRDS(actors.table,
#           file= paste0(imdb.path, "imdb/top250.actors.freq.rds") );

head(actors.table, n=10);
# $name is not any different ever ... 

```
There are 129,300 movies linked to these actors of which 68,784 movies are unique.

### Seed nm5000 (September 2020)

Grab the first 5000 `nmid` values: `nm5000 = 1:5000;` where through the data-collection process, the following were labeled `bad.ones` as they did not have a page (e.g., 404 error or redirect): `bad.ones = c(831, 2176, 2241, 2549, 2740, 2778, 2865, 2896, 3019, 3019, 3236, 3240, 3290, 3429, 3520, 3565, 3598, 3746, 3752, 3908, 4027, 4136, 4176, 4261, 4337, 4339, 4565, 4580, 4593, 4617, 4633, 4783, 4970);`

The resulting vector of `nmid`s is called `actors.nm5000.rds`.

### Seed Headliners (September 2020)

From 68,784 movies above, find the headliners creatives: top-3 actors, writers, directors.  From those, pick the creatives that have at least 15 movies where they were that creative role.

* `glue.movies.headliners.rds` has the info on headliners for 68,784 movies.

* `actors.headliners.rds` are those actors with 15+ movies where they are a headliner.actor

* `headliners.directors.rds` are those directors with 15+ movies where they are a headliner.directors

* `headliners.writers.rds` are those writers with 15+ movies where they are a headliner.writers

Finally, there is a `headliners.companies.rds` with a `coid` with a similar criteria.  These were the seeds to generate an all-in dataset.

### All actors (September 2020)

From the various collection processes, `all.actors` is defined.  The total number appears to be 84,985 of which 68,304 are unique.  

This list will be used to parseActorInfo on the actor landing page such as <https://www.imdb.com/name/nm0000243/> and perform doActorSearch on the actor-film search page(s) such as <https://www.imdb.com/filmosearch/?explore=title_type&role=nm0000243&ref_=filmo_ref_typ&sort=num_votes,desc&mode=detail&page=1&title_type=movie>.

It is the merge of unique `nmid`s from the following:

* `actors.byyear.popular50.rds` [35,245] (by votes)

* `actors.byyear.gem50.rds` [37,997] (by ratings) ... I had `unpopular` and `dud` but chose to exclude them)

* `actors.headliners.rds` [2,407]

* `actors.nm5000.rds` [4,968]

* `actors.top250.rds` [3,092]

* `headliners.directors.rds` [606]

* `headliners.writers.rds` [670]

Recall that `glue.movies.headliners.rds` has the info on headliners for 68,784 movies.  

Looping over this `all.actors` list, three data frames are built:

* `all.actors.rank` is the ranking of the ActorSearch., showing (for that actor), which movies were highest ranked. (e.g., `nmid|rank|ttid` with `nm0675239|9|tt0329022`)

* `all.actors.movies` is a 'movies-info' data frame built from parsing ActorSearch.  The raw file has lots of replicates that will be removed into a final data frame. (e.g., `ttid|year|rated|minutes|ratings|metacritic|votes|millions|title|genre|paragraph` with `tt0007617|1917|NA|80|5.7|NA|NA|NA|Aladdin and the Wonderful Lamp|Fantasy|The story of Aladdin and the Princess Badr al-badr's adventures as told through child actors.` or `tt0038650|1946|PG|130|8.6|89|388818|NA|It's a Wonderful Life|Drama, Family, Fantasy|An angel is sent from Heaven to help a desperately frustrated businessman by showing him what life would have been like if he had never existed.`

* `all.actors.info` is the 'actors-info' dataframe built by parsing the actor's homepage. (e.g., `nmid|name|roles|bio|born.when|born.where|died.when|died.where|starmeter.rank|starmeter.delta` as `nm0169088|Nick Cogley|Actor,Director,Writer|Nick Cogley was born on May 4, 1869 in New York City, New York, USA as Nicholas P.J. Cogley. He was an actor and director, known for Only a Farmer's Daughter (1915), The Dramatic Life of Abraham Lincoln (1924) and Monte Cristo (1912). He died on May 20, 1936 in Santa Monica, California, USA.|1869-5-4|New York City, New York, USA|1936-5-20|Santa Monica, California, USA|NA|270644` or `nm0443857|James Keane|Director,Writer,Actor|James Keane was born on March 23, 1874. He is a director and writer, known for Richard III (1912), Money (1915) and Whispering Women (1921).|1874-3-23|NA|NA|NA|NA|-5693760` or `nm0515975|Ethel Lloyd|Actress|Ethel Lloyd was born on March 23, 1886 in Brooklyn, New York, USA. She was an actress, known for A Florida Enchantment (1914), The Ransom (1916) and Mother's Roses (1915). She was married to Lloyd Hamilton. She died on January 12, 1923 in Brooklyn.|1886-3-23|Brooklyn, New York, USA|1923-1-12|Brooklyn, New York, USA|NA|-58296`

For some reason, the following `nmid`s didn't seem to work: `nm2559854`

### All movies (September 2020)

From the various collection processes, `all.movies` is defined.  It is the merge of unique `ttid`s from the following:

* `movies.byyear.popular50.rds`  (by votes), using `my.movies$ttid` column

* `movies.byyear.gem50.rds` (by ratings), using `my.movies$ttid` column ... I had `unpopular` and `dud` but chose to exclude them)

* `movies.top250.rds`

* `glue.movies.headliners.rds` (from headliners) , using `my.movies$ttid` column.

Looping over this `all.movies` list, four data frames are built:

* `all.movies.creatives` is an update of the creatives info. (e.g., `ttid|nmid|role` as `tt0149676|nm0347890|director` , `tt0149676|nm0214745|writer` , `tt0149676|nm0035250|star` , `tt0149676|nm0040310|star` , `tt0149676|nm1513229|star` ... a possible bug `tt7454890|pro.imdb.com|filmmakers` 

* `all.movies.companies` is an update of the companies info (e.g., `ttid|coid|name` as `tt0884328|co0019626|Dimension Films` , `tt0884328|co0029398|Darkwoods Productions` , `tt0884328|co0150452|The Weinstein Company` 

* `all.movies.extra` contains an at-the-moment unprocessed collection of key-value pairs.  Should be of a panel form:  `ttid|key.name|key.href|key.txt` .  This collects the **Details** from the movie's `filmInfo` landing page.  Currently, `ttid|keys|href|txt`

* `all.movies.actors.characters` contains a link between a movie `ttid` and actor `nmid` and the name of the character played by the actor `character`.  (e.g., `ttid|nmid|character` as `tt0000679|nm0000875|The Wizard of Oz Man` or `tt0000679|nm0933446|Nick Chopper - Tin Woodman /                The White Rabbit` ... notice the `/` which means the actor had multiple characters in the film.  This data needs a bit of cleansing. **Note:** This character information comes from the movies, not directly from the actors.  As a result, some movies returned from ActorSearch will not have the characters.  I do have that information available on the ActorInfo page, just haven't parsed it from there (as it is a potpourri of different types of roles, and I just want films).


### Movie count by year (September 2020)
To build the `top50` lists, I also was able to grab total movie count by year.  This is a small dataframe `moviecount.byyear.rds`.

### Final moves (September 2020)

I added another movies list `movies.tt5000` analogous to `actors.nm5000`.  Since movies can list actors, this also resulted in another `actors.tt5000`.  There were lots of bad movies in this list, so we ended up with 4,942 ... how many are new to the world, at this moment I don't know.  Most `bad.ones` are redirects (301 Moved) or something.

```{r, chunck-tt5000-nm5000, include=TRUE}

bad.ones = c("nm2893280", "nm11424970", "nm0361959",
				"nm1476618", "nm0209637", "nm2559854", 
				"nm0950967", "nm8939460", "nm0579465",
				"nm0562771", "nm0465355", "nm3299108",
				"nm0805389" );


bad.ones = c("tt0003976", "tt0000937", "tt0004183",
			"tt0002957", "tt0004462", "tt0004680",
			"tt0004122", "tt0000600", "tt0001651",
			"tt0000735", "tt0004697", "tt0000702",
			"tt0000311", "tt0003882", "tt0001991",
			"tt0004464", "tt0001433", "tt0000973",
			"tt0000600", "tt0004148", "tt0004203",
			"tt0004388", "tt0003295", "tt0003023",
			"tt0000710", "tt0004113", "tt0003826",
			"tt0000297", "tt0003415", "tt0003769",
			"tt0003383", "tt0004082", "tt0000021",
			"tt0004430", "tt0000136", "tt0004506",
			"tt0004705", "tt0003435", "tt0002784",
			"tt0001958", "tt0004220", "tt0000635",
			"tt0003858", "tt0004014", "tt0003604",
			"tt0003290", "tt0001938", "tt0002032",
			"tt0003430", "tt0004206", "tt0003352",
			"tt0001745", "tt0001953", "tt0002371",
			"tt0002101", "tt0003857", "tt0002275",
			"tt0004556", "tt0004689"
			);

# 
# actors.movies.top250.file = paste0(data.path, "actors.movies.top250.txt");
# actors.movies.top250.df   = utils::read.csv(actors.movies.top250.file, 
#                                           header=TRUE, quote="", sep="|");
# 
# movies.info.top250.file = paste0(data.path, "movies.info.top250.final.txt");
# movies.info.top250.df   = utils::read.csv(movies.info.top250.file, 
#                                           header=TRUE, quote="", sep="|");
# 
# actors.movies.top250.file = paste0(data.path, "actors.movies.top250.txt");
# actors.movies.top250.df   = utils::read.csv(actors.movies.top250.file, 
#                                           header=TRUE, quote="", sep="|");



```


