---
title: "IMDB functions"
output:
  html_document:
    df_print: paged
---

```{r, chunk-setup, include=FALSE}
# include=FALSE means it is running, but invisible ...
knitr::opts_chunk$set(echo = TRUE);
knitr::opts_chunk$set(warning = FALSE);
knitr::opts_chunk$set(message = FALSE);
```

# Documentation of functions

Since `Roxygen` does not allow a wildcard in the documentation `*` as it tries to render it as *bold* or something, I am resigned to write some external documentation for the functions.

```{r, chunck-humanVerseWSU, include=TRUE}

library(humanVerseWSU);

# library(devtools);
# detach(package:humanVerseWSU);
# install_github("MonteShaffer/humanVerseWSU/humanVerseWSU");
# # Choose (3) None to minimize headaches ....
# library(humanVerseWSU);

```

The dataset is large and `?loadDataIMDB` contains some of the information.  See also <http://md5.mshaffer.com/WSU_STATS419/01_imdb-monte.html>

```{r, chunck-loadData, include=TRUE}

loadDataIMDB();  # will populate a global list of data:  imdb.data

```

## IMDB.getMovieInfoFromActorSearch

```{r, chunck-IMDB.getMovieInfoFromActorSearch, include=TRUE}

IMDB.getMovieInfoFromActorSearch("tt2302755");  # who copied whom?

IMDB.getMovieInfoFromActorSearch("tt2334879");

IMDB.getMovieInfoFromActorSearch("tt0038650");  # not found ?? BUG !

```


## IMDB.searchMovieTitle

```{r, chunck-IMDB.searchMovieTitle, include=TRUE}

IMDB.searchMovieTitle("*Kill*", 4:1);

IMDB.searchMovieTitle("*Love*", c("ttid","title","millions") );

IMDB.searchMovieTitle("*monte*", 4:1, ignore.case=TRUE);
IMDB.searchMovieTitle("*monte*", 4:1, ignore.case=FALSE);

IMDB.searchMovieTitle("Romanc*", 4:1 );

```


## IMDB.getPersonInfo

```{r, chunck-IMDB.getPersonInfo, include=TRUE}


IMDB.getPersonInfo("nm0000005");

IMDB.getPersonInfo("nm0000005", 1:4);

IMDB.getPersonInfo("nm0000005", c("name","bio"));

```

## IMDB.getMoviesForPerson

```{r, chunck-IMDB.getMoviesForPerson, include=TRUE}


IMDB.getMoviesForPerson("nm0000071");

IMDB.getMoviesForPerson("nm0000071", 1:5);

IMDB.getMoviesForPerson("nm0000071", c("title","year","ttid","rank"));

```


## IMDB.searchPersonName

```{r, chunck-IMDB.searchPersonName, include=TRUE}



IMDB.searchPersonName("Frank Oz", 1:3);

IMDB.searchPersonName("Sean*", c("nmid","name","born.where") );

IMDB.searchPersonName("*monte*", 1:2, ignore.case=TRUE);

IMDB.searchPersonName("*monte*", 1:2, ignore.case=FALSE);

IMDB.searchPersonName("Denzel*", c(1,2,4) );

```

## IMDB.genericSearch

```{r, chunck-IMDB.genericSearch, include=TRUE}


#Wildcard `*` breaks when rendered in Roxygen

IMDB.genericSearch("*Kentucky*", "bio", 1:2);

IMDB.genericSearch("*Kentucky*", "born.where", 1:2);

IMDB.genericSearch("*Montana*", "born.where", 1:2);

IMDB.genericSearch("*Seattle*", "born.where", 1:2);

# different dataframe

IMDB.genericSearch("*Montana*", "paragraph", 1:3, imdb=imdb.data$all.actors.movies);

merge( IMDB.genericSearch("*Montana*", "character", 1:4, imdb=imdb.data$all.movies.actors.characters), imdb.data$all.actors.movies, by="ttid" );


merge( IMDB.genericSearch("*Jack*Sparrow*", "character", 1:4, imdb=imdb.data$all.movies.actors.characters), imdb.data$all.actors.movies, by="ttid" );



```


## IMDB.getUniqueCharactersForPerson

```{r, chunck-IMDB.getUniqueCharactersForPerson, include=TRUE}

IMDB.getUniqueCharactersForPerson("nm0000136"); # Johnny Depp

IMDB.getUniqueCharactersForPerson(IMDB.searchPersonName("Frank Oz")$nmid[1]);

```

## All movies @ IMDB by year

```{r, chunck-IMDB.plot-by-year, include=TRUE}

plot(imdb.data$moviecount.byyear);

```
